### 2019-09-22 proglog.tex
adds two new speakers and a panel

\subsubsection{Fatima Ebrahimi, Princeton}
Fatima Ebrahimi is a Research Physicist at the PPPL Theory Department
and an Affiliated Research Scholar at the Department of Astrophysical
Sciences, Princeton University. She has many years of experience in theoretical and global computational extended magnetohydrodynamics (MHD) with wide applications to laboratory fusion and astrophysical plasmas. Her main research interests are MHD
stability in fusion plasmas, momentum transport, dynamos, and magnetic reconnection in laboratory fusion and astrophysical plasmas. She has written many papers over a wide range of topics and peer-reviewed journals. She is an elected executive committee member
of the APS Topical Group in Plasma Astrophysics (GPAP), 2018-2021, and program committee member for U.S. Magnetic Fusion Research (MFR) Strategic Directions, 2017-2018. Dr. Ebrahimi is a great choice to have as a speaker on the future of fusion energy.

@@

@@

\subsubsection{Applications for Fusion and Plasma}

>>>>

@@

\subsubsection{Ross Radel, CEO Phoenix, LLC}
Ross is the CEO and a Board of Directors member of Phoenix. He holds a MS and a PhD in Nuclear Engineering from the University of Wisconsin-Madison. He previously worked as the Senior Member of the Technical Staff at Sandia National Laboratories. Ross has extensive experience with nuclear reactors and advanced power conversion systems that are directly applicable to Phoenix’s core technologies. His previous research at the University of Wisconsin focused on high-flux neutron generation for detecting clandestine material, specifically highly enriched uranium. The mission of Radel's company, Phoenix, is to transform nuclear technology to better our world. This mission statement reflects our mission in hosting the student conference well. We believe Dr. Radel would be a great speaker for the future of nuclear technology.

\subsubsection{Greg Piefer, CEO SHINE}
Dr. Piefer is the founder and CEO of SHINE Medical Technologies. The mission of SHINE is to lead the world in safe, clean, and affordable production of medical tracers and treatment elements. He holds a PhD in nuclear engineering, and BS degrees in physics and electrical and computer engineering from the University of Wisconsin–Madison. Greg has received numerous awards and honors including the prestigious UW-Madison Early Career award, is the primary inventor on multiple patents and author or co-author of numerous publications, and serves on the boards of several profit and non-profit entities. His passion is the growth of technology companies that take scientific advancement to commercialization, providing the opportunity to serve and better humanity. Piefer's goals are perfectly attuned to the goals of this conference and he would be an excellent speaker on the powerful applications of radiological engineering.

@@

\subsubsection{Applications for Plasma Processing}

\subsubsection{Fusion: Materials for the Future}
